---
title: "Medicare"
author: "Luciana"
date: "10/24/2019"
output: html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
rm(list = ls())
```


```{r}
library(tidyverse)
library(janitor)
library(arcos)
library(scales)
library(ggrepel)
library(tidycensus)
library(readr)
library(zipcode)
library(viridis)
library(mapview)
library(ggthemes)
```

This project will analyze prescribing rates of health providers that participate in in Medicare Part D (Medicare prescription drug benefit ) program via the Centers for Medicare & Medicaid Services (CMS)  public data set,  Medicare Part D Opioid Prescriber Summary File (2013). Unfortunately there are no databases from part D before 2013 (there are after 2013) . 

Pt1. Opioid prescriptions by practice (specialties prescribing practices rate vs. rate of some high prescription outliers such as family practice and nurse practitioners)

PT.2 comparison of long-term opioid prescriptions (specialties prescribing practices rate vs. rate of some high prescription outliers such as family practice and nurse practitioners)


Part D summary file -

Opioid Claims: The number of Medicare Part D opioid drug claims, including original
prescriptions and refills.
• Long-Acting Opioid Claims: The number of Medicare Part D opioid drug claims that are
considered long-acting, including original prescriptions and refills
• Opioid Prescribing Rate: The number of Opioid Claims divided by the Overall Claims and
multiplied by 100.
• Long-Acting Opioid Prescribing Rate: The number of Long-Acting Opioid Claims divided by the Opioid Claims and multiplied by 100 (so opioid claim count include long acting opiods in it).


good link: 
https://oig.hhs.gov/oei/reports/oei-02-18-00220.pdf


PT 1. 

The Centers for Medicare & Medicaid Services (CMS) has prepared a public data set, the Medicare Part D Opioid Prescriber Summary File, which presents information on the individual opioid prescribing rates of health providers that participate in Medicare Part D program. This file is a prescriber-level data set that provides data on the number and percentage of prescription claims (includes new prescriptions and refills) for opioid drugs, and contains information on each provider’s name, specialty, state, and ZIP code.

This summary file was derived from the 2013 Part D Prescriber Summary Table (Documentation available at: https://www.cms.gov/Research-Statistics-Data-and-Systems/Statistics-Trends-and-Reports/Medicare-Provider-Charge-Data/Downloads/Prescriber_Methods.pdf)


2013 database - https://data.cms.gov/Medicare-Part-D/Medicare-Part-D-Opioid-Prescriber-Summary-File-201/yb2j-f3fp

```{r}

Medicare_Part_D_Opioid_Prescriber_2013 <-read_csv ("data/Medicare_Part_D_Opioid_Prescriber_2013.csv")


Medicare_Part_D_Opioid_Prescriber_2013 <-  Medicare_Part_D_Opioid_Prescriber_2013 %>%
 clean_names()

# Include only States, DC, and Puerto Rico. Remove territories or military locations: "XX" "ZZ" "VI" "MP" "GU" "AS" "AP" "AA" "AE". Then remove unused State factor levels. 

Medicare_Part_D_Opioid_Prescriber_2013 <- subset(Medicare_Part_D_Opioid_Prescriber_2013, !(nppes_provider_state %in% c("XX" ,"ZZ", "VI", "MP", "GU", "AS", "AP", "AA", "AE")))


print(Medicare_Part_D_Opioid_Prescriber_2013)

```


1. What provideres prescribed the highest rates of opioids? What providers has/have highest rates of opioid prescriptions filled (50% + of prescriptions are opioids)

```{r}
# prescriptions above 50% 

 Medicare_Part_D_Opioid_Prescriber_2013%>%
  filter(opioid_prescribing_rate > 50) %>% select(nppes_provider_first_name,nppes_provider_last_name,nppes_provider_zip_code,nppes_provider_state,specialty_description,total_claim_count,opioid_claim_count,opioid_prescribing_rate,long_acting_opioid_claim_count,long_acting_opioid_prescribing_rate) %>% 
  arrange(desc(opioid_prescribing_rate)) %>%
  print(medicare_edited)


```


2. How many of the opioids prescribed were long acting opioids vs short acting opioids (the table does not seperate them)?

```{r}
 
medicare_edited <- Medicare_Part_D_Opioid_Prescriber_2013 %>% mutate(short_acting_opioid_claim_count = opioid_claim_count - long_acting_opioid_claim_count) %>% mutate(short_acting_opioid_prescribing_rate = short_acting_opioid_claim_count / opioid_claim_count * 100 )


```

3. Providers with highest opioid rates + opioids dispensed overall ?

```{r}

medicare_edited %>% 
  arrange(desc(opioid_prescribing_rate)) %>%
  filter(opioid_claim_count>100)


# Louis Jacobsen- WA -607 opiods or 99.84% anesthesiology 
#Michael Kostenko - WV - family practice 152 or 98.06% 
# Lance Ottinger- IN - 180 opioids - 97.30 % nurse practitioner 


```


4. What practictioners have an opioid prescribing rate over 90%? 

```{r}

medicare_edited %>% 
  arrange(desc(opioid_claim_count, opioid_prescribing_rate)) %>%
  filter(opioid_prescribing_rate>90)

# nurse practionter rate of	96.02	 
#podiatry ? very high rate ? 

# high rates (above 90%) and high amounts dispensed - in OH by John Beresh - 
#Thomas Brummett- IL - 	Interventional Pain Management 
# Andrzej Zielke - PA - 	Anesthesiology 
```

5. what professions have highest opioid dosage rate?  - When you join total specialties in a field (speciality_types) and specialists who prescribe high dosages of opioids (high_prescribing_doctors) (so above 50%) you  see some high rates are interventional pain management, pain management and orthopedic surgery. Do these professions require high opioid dosages, or if there is another reason? Why such high prescription rates? 

highlights- 

- nurse practitioner with 185 claim count  but 97.30% are opioids 

- family practice with 155 claim count but 98.06% are opioids
 
- 	Nurse Practitioner	1207 claim count 96.02% opiods  ? 	4 	47711 - Patricia Borst 

articles that speak on  https://scienceofcaring.ucsf.edu/research/nps-and-opioid-prescribing-what-don’t-we-know  - "The information matters because nurse practitioners (NPs) account for the third-largest share of opioids prescribed in primary care, the practice setting that accounts for the largest percentage of opioid prescriptions in the U.S. In rural areas – where NPs are often the only primary care providers providing services to vulnerable populations – the opioid epidemic has been particularly fast-growing." 
 -  https://www.ncbi.nlm.nih.gov/pubmed/25896191


6 - why are there outliers such as nurse practitioners or family doctors (certain practices) that have such high opioid prescribing rates when overall this field does not prescribe much opioids? look at these specific cases. Considering that these professions have a low rate (nurse = 0.015 and family medicine is 0.004 or 3 out of 635 prescribed very high , why?  )


```{r}
#total speciality types 

speciality_types <- Medicare_Part_D_Opioid_Prescriber_2013 %>%
  group_by(specialty_description) %>%
  summarise(total_specialists=n())

# grabs medicare_edited (which grabs only opioid prescribing rate over 50%) and filters claim count over 100 opioids, arranges descending by opioid prescribing rate and groups by speciality.   

high_prescribing_doctors <- medicare_edited %>% 
  arrange(desc(opioid_prescribing_rate)) %>%
  filter(opioid_claim_count>100) %>%
  group_by(specialty_description) %>%
  summarise(high_prescribing_specialists = n()) %>%
  arrange(desc(high_prescribing_specialists))


  speciality_prescriptions_join <- high_prescribing_doctors %>%
  inner_join(speciality_types) %>% 
  mutate( rate = high_prescribing_specialists/total_specialists)%>%
  arrange(desc(rate))
  
  options(scipen = 999)
  
  print(speciality_prescriptions_join)
  
  
 #speciality_prescriptions_join is a join between total specialities in a field (speciality_types) and specialists who prescribe high dosages of opioids (high_prescribing_doctors) (so above 50%). When you do this join you can see some high rates are interventional pain managment, pain management and orthopedic surgery. 
 
 #Would have to see if these professions require high opioid dosages, or if there is another reason. 
 
 #futhermore, would be interesting to look at individual prescribers ( such as nurse practioner and family doctos) and find outliers of high prescriptions, considering that these professions have a low rate (nurse = 0.015 and family medicine is 0.004 or 3 out of 635 prescribed very high , why?  )

```


7. Are there any outliers in practicers that have high opioid prescribing rates when overall field is low ?

```{r}

medicare_edited %>% 
  arrange (desc(opioid_claim_count))%>%
  filter(opioid_claim_count>100, opioid_prescribing_rate > 96)

# Patrica Borst  47711 IN 	Nurse Practitioner 

```
 

8. Which states prescribed the most opioids? 

Join- 
how to get state abbreviation or state to show up as name? if not join will not work. 


```{r}
 
medicare_opioids_state_2013 <- medicare_edited %>% 
  group_by(nppes_provider_state) %>%
  summarise(total_opioids_2013 = n()) %>% arrange(desc(total_opioids_2013)) %>% abbr2state(abbr) %>% print(medicare_opioids_state)

# CA	109563 
# NY	85841 
# TX	64950  

```

9. high prescribers in CA, NY and TX ? Why do these states have such high dosages compared to other states? Especially CA?
 
```{r}
medicare_edited %>% filter (nppes_provider_state == "CA") %>% arrange(desc(opioid_claim_count))

```

```{r}
medicare_edited %>% filter (nppes_provider_state == "NY") %>% arrange(desc(opioid_claim_count))
```

```{r}
medicare_edited %>% filter (nppes_provider_state == "TX") %>% arrange(desc(opioid_claim_count))
```


10. how would I group by long term and short term opioids as well? I would like to compare opioids short -term / long -term sent out in a map, as according to certain research long-acting-opioids is not beneficial. Ive tried and it is not grouping properly. 


11. Pills per person sent out through medicare opioids data by state - 
In other words, do those states where prescribers stand out with high prescriptions also have high pills per person? 
Unable to do this as state is abbreviated in one and not the other. 

Join- 

```{r}
# Define API Key
census_api_key("549950d36c22ff16455fe196bbbd01d63cfbe6cf")

# If you need to look up variables, this is how you do it
acs_variables <- load_variables(2017, "acs5" )

```

```{r}
#get female and males medicare and group into one sum of population by medicare
# 10 is male medicare over 65+ / 20 is female medicare over 65+


acs_medicare_pivot_2013 <- get_acs(geography= "state", variables = c("C27006_010", "C27006_020"), geometry =  FALSE, survey ="acs5", year = 2017) %>%
  select(-moe)%>%
  pivot_wider(values_from=estimate,names_from = variable) %>%
  mutate(total_medicare=C27006_010+C27006_010)%>%
  select(NAME, total_medicare)
```

```{r}

# join two together (medicare + population)

medicare_population_opioids_2013 <- medicare_opioids_state_2013 %>%
  inner_join (acs_medicare_pivot_2013 , by=c ("nppes_provider_state"= "NAME")) %>% 
print (medicare_population_opioids_2013) 


#how to abbreviate state name 
```
 

``` {r}

medicare_population_opioids_2013 <-medicare_population_opioids_2013 %>% 
  mutate(opioids_per_person = opioid_claim_count/total_medicare) 
  
#not working

``` 

12. Comparison of 2013, to 2017. Has opiods prescribed to seniors increased or decreased? Opioids prescribed have increased. - they have increased. I would like to map this to compare with 2013- maybe more years to follow trend. 

```{r}

#2017 

Medicare_Part_D_Opioid_Prescriber_2017 <-read_csv ("data/Medicare_Part_D_Opioid_Prescriber_2017.csv")


Medicare_Part_D_Opioid_Prescriber_2017 <-  Medicare_Part_D_Opioid_Prescriber_2017 %>%
 clean_names()

# Include only States, DC, and Puerto Rico. Remove territories or military locations: "XX" "ZZ" "VI" "MP" "GU" "AS" "AP" "AA" "AE". Then remove unused State factor levels. 

Medicare_Part_D_Opioid_Prescriber_2017 <- subset(Medicare_Part_D_Opioid_Prescriber_2017, !(nppes_provider_state %in% c("XX" ,"ZZ", "VI", "MP", "GU", "AS", "AP", "AA", "AE")))


print(Medicare_Part_D_Opioid_Prescriber_2017)

``` 


```{r}

medicare_opioids_state_2017 <- Medicare_Part_D_Opioid_Prescriber_2017 %>% 
group_by(nppes_provider_state) %>%
summarise(total_opioids_2017 = n()) %>% arrange(desc(total_opioids_2017)) %>% print(medicare_opioids_state)



# OPIOIDS HAVE INCREASED 
``` 



ZIP CODES THAT HAVE HIGH PRESCRIPTIONS 
Zip codes are not grouping properly - nor is it allowing me to group by long-term opioids and short-term opioids
(zip codes are appearing more than once)

13. What specific zip codes have highest perscription in total? Currently unable to view this as it is not grouping properly. I would also like to see which zip codes have high long term opioid percriptions and short-term opioid prescriptions, then compare to 2017, to see if overall trend has been towards more long -term or short-term opioids. 

```{r}

medicare_edited %>% 
  group_by(nppes_provider_zip_code,nppes_provider_state, opioid_claim_count) %>%
  summarise(total_opioids = n()) %>% select( nppes_provider_zip_code,total_opioids) %>% arrange(desc(total_opioids))

# medicare_opioids_zip_count <- medicare_edited %>% group_by(nppes_provider_zip_code, opioid_claim_count) %>% summarise(long_acting_opioids_per_zip = sum(long_acting_opioid_claim_count), short_acting_opioids_per_zip = sum(short_acting_opioid_claim_count)) %>%arrange(desc(opioid_claim_count))


```

14. Pills per person sent out through medicare opioids data, specifically in those high prescribing zip codes? 
 In other words, do those zip codes where prescribers stand out with high prescriptions also have high pills per person? 
 Who is prescribing in those zip codes?  
 
Join- 

```{r}
# Define API Key
census_api_key("549950d36c22ff16455fe196bbbd01d63cfbe6cf")

# If you need to look up variables, this is how you do it
acs_variables <- load_variables(2017, "acs5" )

```

```{r}
#get female and males medicare and group into one sum of population by medicare (zctas)
# 10 is male medicare over 65+ / 20 is female medicare over 65+


acs_zcta_medicare_pivot <- get_acs(geography= "zcta", variables = c("C27006_010", "C27006_020"), geometry =  FALSE, survey ="acs5", year = 2017) %>%
  select(-moe)%>%
  pivot_wider(values_from=estimate,names_from = variable) %>%
  mutate(total_medicare=C27006_010+C27006_010)%>%
  select(GEOID,NAME, total_medicare)
```

```{r}

# join two together (medicare + population)

medicare_population_opioids_zip <-medicare_opioids_zip_count %>%
  inner_join(acs_zcta_medicare_pivot, by=c ( "nppes_provider_zip_code" = "GEOID"))%>%
  filter (total_medicare !=0)

```

I tried to group as well by long acting opioids per zip, short acting opioids per zip- as I wanted to compare these trends *since long acting opioids are not recommended. 


*also want to compare long-acting opioids to trend in 2017. 

``` {r}

medicare_population_opioids_zip <- medicare_population_opioids_zip %>% 
  mutate(opioids_per_person = opioid_claim_count/total_medicare,
         long_acting_opioids_per_person = long_acting_opioids_per_zip/total_medicare,
         short_acting_opioids_per_person = short_acting_opioids_per_zip/ total_medicare)%>%
  select (nppes_provider_state, nppes_provider_zip_code, opioid_claim_count, long_acting_opioids_per_zip, short_acting_opioids_per_zip, total_medicare, opioids_per_person,long_acting_opioids_per_person, short_acting_opioids_per_person)


# how are there some locations with medicare population of only 2 people but mutliple prescribers, is this an error ?  

``` 

15.Locations (zip codes ) with high counts of opioids per person? High counts of long-acting opioids, short acting opioids? map this out to compare trends in long acting vs short acting. 

```{r}

medicare_population_opioids_zip %>% arrange(desc(opioids_per_person))
```  
  


PART 2- 

Long- acting Opioids -

WOULD LIKE TO COMPARE LONG TERM OPIOID TREND WITH SHORT-TERM OPIOID TREND /// comparison of 2013 to 2017 to see if long actin gopioids have increased, as well as overall opioids increased. 

The number of Medicare Part D opioid drug claims that are considered long-acting, including original prescriptions and refills. For a list of drugs that include long-acting opioids, visithttps://www.cms.gov/Research-Statistics-Data-and-Systems/Statistics-Trends-and-Reports/Medicare-Provider-Charge-Data/Downloads/OpioidDrugList.zip.


What are long acting opioids? ( long_acting_opioid_claim_count field in database) 

Long-acting opioid -  https://www.drugabuse.gov/sites/default/files/files/CommonlyUsedLAOpioids.pdf

https://www.cdc.gov/vitalsigns/opioids/index.html - the CDC states : " Taking opioids for longer periods of time or in higher doses increases the risk of addiction, overdose, and death." 


Examples of long-acting opioids
Fentanyl patch (Duragesic)
Methadone (Dolophine)
Morphine (Kadian)
Oxycodone controlled-release (OxyContin)
(https://www.uofmhealth.org/health-library/abo7833)

https://www.ajmc.com/journals/supplement/2015/ace0029_aug15_painrems/ace0029_aug15_painrems_ray 

Opioid Claims: The number of Medicare Part D opioid drug claims, including original
prescriptions and refills.
• Long-Acting Opioid Claims: The number of Medicare Part D opioid drug claims that are
considered long-acting, including original prescriptions and refills
• Opioid Prescribing Rate: The number of Opioid Claims divided by the Overall Claims and
multiplied by 100.
                  
• Long-Acting Opioid Prescribing Rate: The number of Long-Acting Opioid Claims divided by the Opioid Claims and multiplied by 100.


-  Comparison of rate of opioid use to long-term use opioids in 2013 
-  who prescribes the most long term opioids - what field ?
-  any outliers in long -term opioids prescribed? 
- comparing death rates to long term opiods used in states, do they go up compared to overall trend? 

```{r}

medicare_edited %>% 
  arrange(desc(long_acting_opioid_prescribing_rate)) %>%
  filter(long_acting_opioid_claim_count>100)

#rey ximenes- TX- 
# 5 practitioners in PA are among high opioid prescriber above 100 opioiids dispensed - 2 of them seem to be related Lodico but work in different department Anesthesiology and interventional pain management 
# louis jacobsen - in WA also amongst high long term prescribers  


```


```{r}

medicare_edited %>% 
  arrange(desc(long_acting_opioid_claim_count, long_acting_opioid_prescribing_rate)) %>%
  filter(long_acting_opioid_prescribing_rate>90)

# - individual supplier Mark Lodico again - in PA prescribed 4757 opioids, 4591 of which were long acting opioids (interventional pain management. 

# Richard Plowey nuerology- 2774 opioids prescribed- 2673 were long acting - or 96.36% nuerology- 

# Laura Bye - nurse practionter rate of	96.02	in long-term opioids


```


```{r}


#total speciality types 

speciality_types <- Medicare_Part_D_Opioid_Prescriber_2013 %>%
  group_by(specialty_description) %>%
  summarise(total_specialists=n())

# grabs medicare_edited (which grabs only opioid prescribing rate over 50%) and filters claim count over 100 opioids, arranges descending by opioid prescribing rate and groups by speciality.   

high_prescribing_long_term_doctors <- medicare_edited %>% 
  arrange(desc(long_acting_opioid_prescribing_rate)) %>%
  filter(long_acting_opioid_claim_count>100) %>%
  group_by(specialty_description) %>%
  summarise(high_prescribing_long_term_specialists = n()) %>%
  arrange(desc(high_prescribing_long_term_specialists))


  speciality_prescriptions_long_term_join <- high_prescribing_long_term_doctors %>%
  inner_join(speciality_types) %>% 
  mutate( rate = high_prescribing_long_term_specialists/total_specialists)%>%
  arrange(desc(rate))
  
  options(scipen = 999)
  
  print(speciality_prescriptions_long_term_join)
  
  
 
 
 #s speciality_prescriptions_long_term_join is a join between total specialities in a field (speciality_types) and specialists who prescribe high dosages of long term opioids (high_prescribing_long_term_specialists) (so above 50%). When you do this join you can see some high rates are interventional pain managment, pain management and  anesthesiology, this keeps in line with high prescribers of regular opioids, where high prescribers were in interventional pain management, pain managament BUT orthopedic surgery (Anesthesiology was 0.18615722656 rate in normal opioids vs long term anesthosiology rate of 0.13403320312 ). 
 
 
 # Long term opioids tend to have lower rates than normal opioids. 
 
 
 #Would have to see if these professions require high opioid dosages, or if there is another reason. 
 
 # again specialties that lie on lower end but have outliers?  
  
# individual supplier Mark Lodico again - in PA prescribed 4757 opioids, 4591 of which were long acting opioids (interventional pain management. 

# Richard Plowey nuerology- 2774 opioids prescribed- 2673 were long acting - or 96.36% nuerology- 

# Laura Bye - nurse practionter rate of	96.02	in long-term opioids - rate 0.00882130211 862 high prescribers out of 97718 specialists 


```


